Investigating the outer reaches of the Sculptor and Ursa Minor dwarf galaxies

### 2025-07-21 thesis/appendix.tex
introduction updates

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{/Users/daniel/thesis_2/figures/scl_density_methods_extra.pdf}}
\caption[Scl density comparison]{Density profiles for various
assumptions for Sculptor. PSAT is our fiducial 2-component J+24 sample,
circ is a 2-component bayesian model assuming circular radii, simple is
the series of simple cuts described, bright is the sample of the
brightest half of stars (scaled by 2), DELVE is a sample of RGB stars
(background subtracted and rescaled to
match).}\label{fig:scl_density_extras}
\end{figure}

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{/Users/daniel/thesis_2/figures/scl_density_methods_j24.pdf}}
\caption[Scl density methods]{Comparison of density profiles for each
J+24 method. The fiducial is a 2-component elliptical model. However,
the 1-component is still elliptical but only contains 1 component and
the circular model assumes a circular outer density profile and bins in
circular bins instead of elliptical
bins.}\label{fig:scl_density_j24_methods}
\end{figure}

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{/Users/daniel/thesis_2/figures/umi_density_methods_extra.pdf}}
\caption[UMi density comparison]{Similar to
Fig.~\ref{fig:scl_observed_profiles} except for Ursa
Minor}\label{fig:umi_density_extras}
\end{figure}

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{/Users/daniel/thesis_2/figures/umi_density_methods_j24.pdf}}
\caption[UMi density methods]{Similar to
Fig.~\ref{fig:scl_density_j24_methods} except for Ursa
Minor.}\label{fig:umi_density_j24_methods}
\end{figure}

>>>>

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/scl_density_methods_extra.pdf}}
\caption[Scl density comparison]{Density profiles for various
assumptions for Sculptor. PSAT is our fiducial 2-component J+24 sample,
circ is a 2-component bayesian model assuming circular radii, simple is
the series of simple cuts described, bright is the sample of the
brightest half of stars (scaled by 2), DELVE is a sample of RGB stars
(background subtracted and rescaled to
match).}\label{fig:scl_density_extras}
\end{figure}

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/scl_density_methods_j24.pdf}}
\caption[Scl density methods]{Comparison of density profiles for each
J+24 method. The fiducial is a 2-component elliptical model. However,
the 1-component is still elliptical but only contains 1 component and
the circular model assumes a circular outer density profile and bins in
circular bins instead of elliptical
bins.}\label{fig:scl_density_j24_methods}
\end{figure}

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/umi_density_methods_extra.pdf}}
\caption[UMi density comparison]{Similar to
Fig.~\ref{fig:scl_observed_profiles} except for Ursa
Minor}\label{fig:umi_density_extras}
\end{figure}

\begin{figure}
\centering
\pandocbounded{\includegraphics[keepaspectratio]{figures/umi_density_methods_j24.pdf}}
\caption[UMi density methods]{Similar to
Fig.~\ref{fig:scl_density_j24_methods} except for Ursa
Minor.}\label{fig:umi_density_j24_methods}
\end{figure}
